### 2019-07-11 paper/paper.tex
Update the paper and the toml files

However, as usual it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++. This provides the primary motivation towards the development of RayTracer.jl. We develop an entire general purpose ray tracer in a high level numerical computation language. The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer.

@@

\todo[inline]{Add graphs comparing finite differencing to AD}

>>>>

However, as usual it is difficult to compute efficient derivatives from a production-ready renderer, typically written in a performance language like C++. This provides the primary motivation towards the development of RayTracer.jl. We develop an entire general purpose ray tracer in a high level numerical computation language. The presence of strong automatic differentiation libraries like Zygote.jl make it trivial to compute efficient derivatives from the renderer. We present the performance gains we get on using Zygote as compared to Central Differencing in Figure~\ref{fig:ad_perf}.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth, height=150px]{images/differentiation.png}
    \caption{Performance Comparison between Zygote AD and Numerical Differentiation}
    \label{fig:ad_perf}
\end{figure}

@@
